### 2025-04-09 multiple-regression.qmd
20250408 - non-independence

>>>>

Please note that the $p$-value for regression coefficients assumes that the observations are independent—in particular, that the residuals are not correlated.
However, the observations are not independent in the `player_stats_seasonal` dataframe used above, because the same player has multiple rows—one row corresponding to each season they played.
This non-independence violates the traditional assumptions of the significance of regression coefficients.
We could address this assumption by analyzing only one season from each player or by estimating the significance of the regression coefficients using cluster-robust standard errors.
For simplicity in the models above, we present results above from the whole dataframe.
In @sec-mixedModels, we discuss [mixed model](#sec-mixedModels) approaches that handle repeated measures and other data that violate assumptions of non-independence.
Below, we demonstrate how to account for non-independence of observations using cluster-robust standard errors.
